Fractional anisotropy as an optimal tracer of cosmic voids

### 2014-07-31 cosmic_voids.tex
Adding motivation to the introduction

We present here a novel approximation for finding voids in cosmological 
simulations based upon two different schemes commonly used for quantifying
the cosmic web, i.e. the T-web and the V-web (the so-called web schemes), 
which have proven to be very adequate for that purpose. Unlike previously 
defined void finding techniques based on the density field, we use here 
the fractional anisotropy (FA) computed from the eigenvalues of each web 
scheme and then, through a Watershed Transform, we identify individual 
voids as the catching basins of local minima of the FA field. Like other 
Watershed Transform-based schemes, ours retains the same advantages, i.e., 
it is relatively free-parameter and makes no significant assumptions on 
the shape and structure of voids.

We test our method on the Bolshoi simulation and compare it with a
density-based scheme. We find our method gives a better resemblance to the
visual impression of the cosmic web in addition to a more robust 
description of voids as it allows to identify, in a very clear manner, 
their spatial limits as regions where the FA is maximized, normally 
corresponding to walls and filaments. This is mainly because of the 
non-monotonic behaviour of the FA, what allows to use it as a sort of 
one-dimensional tomography of the cosmic web.

@@

Since voids where discovered in the first compiled galaxy surveys 
\citep{Chincarini75, Gregory78, Einasto80M, Einasto80N, Kirshner81, 
Kirshner87}, they have been identified, along with the filamentary and 
hierarchically clustered nature of the cosmic web, as one of the most 
striking features of the Megaparsec Universe \citep{Bond96}. Nevertheless,
due to the large volume extension of void regions ($\sim 5-10\ \mbox{Mpc} 
h^{-1}$), statistically significant catalogues of voids \citep{Pan10, 
Sutter12b, Nadathur14} only have become available after modern large 
galaxy surveys like the two-degree field Galaxy Survey \citep{Colless01,
Colless03} and the Sloan Digital Sky Survey \citep{York00,Abazajian03}, 
thereby triggering a plethora of more refined observational and 
statistical studies of voids throughout the last decade \citep{Hoyle04,
Croton04, Rojas05, Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b, 
Tikhonov07, BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}

On the theoretical side, early descriptions of the evolution of the 
large-scale Universe, leaded by the seminal work of \citet{Zeldovich70}, 
are highly consistent with the cosmic web picture, where planar 
pancake-like regions of matter enclose enormous sub-dense voids and are 
bordered, in turn, by thin filaments and high-density clumpy knots. First
theoretical models for describing formation, dynamics and properties of
voids \citep{Hoffman82, Icke84, Bertschinger85, Blumenthal92} were quickly
complemented and extended by first numerical studies based on simulations
\citep{Martel90, Regos91, Weygaert93, Dubinski93}. This tendency of using
numerical data from N-body simulations, fuelled by last generation 
computing systems, has become increasingly common in the last years as a 
powerful analysis toolkit of cosmic voids (for an extensive compilation of 
previous numerical works, see \citet{Colberg08}).

>>>>

We present here a novel approximation for finding voids in cosmological 
simulations based upon two different schemes commonly used for quantifying
the Cosmic Web, i.e. the T-web and the V-web (the so-called web schemes), 
which have proven to be very adequate for that purpose. Unlike previously 
defined void finding techniques based on the density field, we use here 
the fractional anisotropy (FA) computed from the eigenvalues of each web 
scheme and then, through a Watershed Transform, we identify individual 
voids as the catching basins of local minima of the FA field. Like other 
Watershed Transform-based schemes, ours retains the same advantages, i.e., 
it is relatively free-parameter and makes no significant assumptions on 
the shape and structure of voids.

We test our method on the Bolshoi simulation and compare it with a
density-based scheme. We find our method gives a better resemblance to the
visual impression of the Cosmic Web in addition to a more robust 
description of voids as it allows to identify, in a very clear manner, 
their spatial limits as regions where the FA is maximized, normally 
corresponding to walls and filaments. This is mainly because of the 
non-monotonic behaviour of the FA, what allows to use it as a sort of 
one-dimensional tomography of the Cosmic Web.

@@

Since voids where discovered in the first compiled galaxy surveys 
\citep{Chincarini75, Gregory78, Einasto80M, Einasto80N, Kirshner81, 
Kirshner87}, they have been identified, along with the filamentary and 
hierarchically clustered nature of the Cosmic Web, as one of the most 
striking features of the Megaparsec Universe \citep{Bond96}. Nevertheless,
due to the large volume extension of void regions ($\sim 5-10\ \mbox{Mpc} 
h^{-1}$), statistically significant catalogues of voids \citep{Pan10, 
Sutter12b, Nadathur14} only have become available after modern large 
galaxy surveys like the two-degree field Galaxy Survey \citep{Colless01,
Colless03} and the Sloan Digital Sky Survey \citep{York00,Abazajian03}, 
thereby triggering a plethora of more refined observational and 
statistical studies of voids throughout the last decade \citep{Hoyle04,
Croton04, Rojas05, Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b, 
Tikhonov07, BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}

On the theoretical side, early descriptions of the evolution of the 
large-scale Universe based on gravitational instabilities in primordial 
stages and leaded by the seminal work of \citet{Zeldovich70}, are highly 
consistent with the Cosmic Web picture, where planar pancake-like regions 
of matter enclose enormous sub-dense voids and are bordered, in turn, by 
thin filaments and high-density clumpy knots. First theoretical models for 
describing formation, dynamics and properties of voids \citep{Hoffman82, 
Icke84, Bertschinger85, Blumenthal92} were dramatically complemented and 
extended by first numerical studies based on simulations \citep{Martel90, 
Regos91, Weygaert93, Dubinski93}. This tendency of using numerical data 
from N-body simulations, fuelled by last generation computing systems and
ever more efficient numerical algorithms, has become increasingly common 
in the last years as a powerful analysis toolkit of cosmic voids (for an 
extensive compilation of previous numerical works, see \citet{Colberg08}).

At present, studying voids may be considered as a threefold enterprise: 
first, they are a key ingredient of the Cosmic Web as they dominate almost 
the entire volume distribution at large-scales and additionally, they 
compensate over-density structures in the total budget of matter. This 
implies that a full understanding of their dynamics and properties is 
essential for fathoming the high complexity of the Cosmic Web. Second, 
they provide a valuable resource for inferring and probing cosmological 
parameters as their structure and dynamics are highly determined by these 
values. Third, they constitute and unique and still largely pristine 
environment in which can be tested and probed theories of galaxy formation 
and evolution.
